---
title: "Using dplyr to fix mistakes"
author: "Aubrey Ahern"
date: "10/2/2022"
output: html_document
---

#My goals for the assignment is to be more independent in problemshooting errors within R and also to become more comfortable with dplyr functions (and their parameters).

#Clear R's Brain...
```{r}
rm(list = ls())
```

#Turn on dplyr, here, and ggplot2 packages (no need to install)
```{r}
library(dplyr)
library(here)
library(ggplot2)
```

#Import data without using stringsAsFactors
#summary(DF)

#Import data using stringsAsFactors
#View data using View()
```{r}
DF <-read.csv(here("Data", "drug_resistance.csv"), stringsAsFactors = TRUE)
summary(DF)
```

#importing my data using stringsAsFactors makes it so that the strings within the dataset are considered factors whereas the other method leaves them as plain strings

#Thus summary is able to be more accurate and useful to the user when there are explicit factor variables

```{r}
tech_name = select(DF, tech.name)
unique(tech_name, incomparables = FALSE, fromLast = FALSE, nmax = NA)
```

#I see an error when I try to use levels() on factor variables

#Even after looking through GSWR, I am not sure how to repair the number of factor variables but hope to learn in class.


