---
title: "Applying More dplyr to my Data"
author: "Aubrey Ahern"
date: "9/28/2022"
output: html_document
---

#My goals for the assignment is to be more independent in problemshooting errors within R and also to become more comfortable with dplyr functions (and their parameters).

#Clear R's Brain...
```{r}
rm(list = ls())
```

#Turn on dplyr, here, and ggplot2 packages (no need to install)
```{r}
library(dplyr)
library(here)
library(ggplot2)
```

#Import data using stringsAsFactors
#View data using View()
```{r}
DF <-read.csv(here("Data", "day_one_data_for_homework13.csv"), stringsAsFactors = TRUE)
View(DF)
```

#Importing the .csv file changed the special character in the column heading to "..."
#Let's rename column headers to be easier to work with in R using the names() function
```{r}
names(DF) <- c("Name", "Date", "Part", "Tree_num", "Species", "leaf_length", "leaf_width", "leaf_units")
```

#Select just the rows of data that are in English units (inches) and that save them to a new data frame called "English"
```{r}
English <- filter(DF, leaf_units == "inches")
```

#Collect all of the data for which the dates have been formatted in the same way and put in a single data frame and called "Uniform_dates"
```{r}
Uniform_dates <- filter(DF, Date == "8/24/2022")
Uniform_dates
```



