---
title: "Ahern_HW11_GSWRCh3Ex1"
author: "Aubrey Ahern"
date: "9/25/2022"
output: html_document
---

#In this Homework we will be exploring the dplyr package and how it can be used to visualize and extract data.

#Clear R's Brain...
```{r}
rm(list = ls())
```

#Libraries I need (no need to install...)
```{r}
library(dplyr)
library(ggplot2)
```

#Now suck in some data
```{r}
DF <- read.csv(here("Data", "compensation.csv"))
```

#Quick Summary
```{r}
summary(compensation)
```

#Using dyplr, always takes and gives a data frame

#Columns
```{r}
select(compensation, Fruit) #gets the Fruit Column
select(compensation, -Root) #take Root column out from data
```

#Rows
```{r}
slice(compensation, c(2, 3, 10)) #gets the 2nd, 3rd, and 10th rows
```

#Gets rows for each condition, and assigns to an object
```{r}
lo_hi_fruit <- filter(compensation, Fruit > 80 | Fruit < 20)
```

#Run this to see what the above line "saved" for later use.
```{r}
lo_hi_fruit
```

#What does compensation look like now?
```{r}
head(compensation)
  #use mutate
  #log(Fruit) is in the column logFruit all of which gets pub into the object              compensation
compensation <- mutate(compensation, logFruit = log(Fruit))

  #first 6 rows of the new compensation
head(compensation)
```

```{r}
arrange(compensation, Fruit)
```

#Root values from Fruit > 80 subset
```{r}
select(filter(compensation, Fruit > 80), Root)
```

#Root values from Fruit > 80 subset via piping
```{r}
compensation %>%
  filter(Fruit > 80) %>%
    select(Root)
```

#Use one grouping variable(grazing) and two levels... asking for means
```{r}
summarize(
  group_by(compensation, Grazing), 
  meanFruit = mean(Fruit))
```

```{r}
compensation %>%
  group_by(Grazing) %>%
    summarise(meanFruit = mean(Fruit))
```

```{r}
compensation %>%
  group_by(Grazing) %>%
    summarise(
      meanFruit = mean(Fruit),
      sdFruit = sdFruit)
```