---
title: "Ahern_Homework12.Rmd"
author: "Aubrey Ahern"
date: "9/26/2022"
output: html_document
---

#Clear R's Brain...
```{r}
rm(list = ls())
```

#Turn on dplyr and here packages (no need to install)
```{r}
library(dplyr)
library(here)
library(ggplot2)
```

#Import data using stringsAsFactors
```{r}
Cover <-read.csv(here("Data", "donnerville_percent_cover.csv"), stringsAsFactors = TRUE)
```

```{r}
glimpse(Cover) #shows you the data
head(Cover) #first six rows of data
str(Cover) #displays the structure of dataframe
tail(Cover) #last six rows of data
names(Cover) #column headers
```

#Select the Slope column in order to be examined
  #Examine Slopes using summary() which returns the min, 1st quartile, median, mean, 3rd quartile, and max
```{r}
slopes <- select(Cover, Slope)
summary(slopes)
```

#Filter the data by only selecting pieces of data at site 3 and storing them in variable "site3"
```{r}
site1 <- filter(Cover, Site == "Donnerville 1")
site1
```

#Renaming improper column headings using dplyr rename() function
```{r}
Cover <- Cover %>% rename(Plot_type = Plot.type, Plot_dim = Plot.dim)
names(Cover)
#other method
#names(Cover) <- c("Site", "Date", "Plot_type", "Plot_dim", "Slope", "Aspect", "Plot", "Type", "Percent")
```

#Determine the average percent cover by cover type for Donnerville 1
  #mean() is in the base package
```{r}
Cover %>% filter(Site == "Donnerville 1") %>% group_by(Type) %>% summarise(
  avg_percent_cover = mean(Percent)
  )
```

#Determine the average percent vascular plant cover across all sites
```{r}
PerCov <- Cover %>% filter(Type == "Vascular") %>% summarise(
  avg_percent = mean(Percent)
)
```

