---
title: "Homework 26"
author: "Aubrey Ahern"
date: "11/2/2022"
output: html_document
---

```{r}
rm(list = ls())
library(tidyverse)
library(here)
library(ggfortify)
```

pull in the data
```{r}
soil <- read.csv(here("Data", "soil_reduced-1.csv"), stringsAsFactors = TRUE)
```

Before we begin any analysis, we need to check out data for possible errors/outliers. Let's begin with that.

A. Forest Names
```{r}
levels(soil$Forest)
```

B. Let's check the soil organic matter and soil calcium
  Start with a histogram for SOM
```{r}
ggplot(soil, aes(x = SOM_percent)) + geom_histogram()
```

Now check soil calcium
```{r}
ggplot(soil, aes(x=Ca_ppm))+ geom_histogram()
```

Let's also just run a summary on all the variables
```{r}
summary(soil)
```


*SCATTER PLOT*
#The influence of a single point on the relationship is called "leverage"
From looking at the data, it appears there may be a weak positive relationship b/w SOM and Ca

Can I guess the slope or y-intercept?
Slope c. 1000/53 = 18ish, y-int c. 0? right around there.

What statistical model fits these data?
Both response and predictor are continuous so linear regression seems appropriate

So, let's construct the model
```{r}
SOM_CA_mod <- lm(Ca_ppm~SOM_percent, data = soil)
```

Now I need to check model assumptions before interpreting
```{r}
autoplot(SOM_CA_mod)
```

Assumptions of linear regression (including ANOVA)
1. Data are normally distributed aka fit the :normal distribution"
2. Variance if residuals is even

Based on my observations of the auto plot results I am modestly comfortable that my data meet the lms assumptions
Now look at model outcome
```{r}
anova(SOM_CA_mod)
```



QUESTIONS
1. Is there a relationship between Soil organic matter (SOM, %) and soil calcium (Ca_ppm)?

2. Does the abundance of worms differ between Donnerville and the Kip Tract?

3. Does the abundance of soil Magnesium (Mg_ppm) differ between Peavine and South Hammond?

4. Does the abundance of zinc (Zn_ppm) differ among forests?

